TBD

### 2021-02-20 outputs/paper/paper.Rmd
Update pie chart colour theme

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
library(dplyr)
library(palettetown)
library(wesanderson)
library(RColorBrewer)
library(ggthemes)
library(scales)
library(broom)
library(purrr)

@@

### Create pie chart
ggplot(dfBoroughs, aes(x="", y = prop, fill = group)) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  coord_polar("y", start = 0) +
  theme_void() +
  geom_text(aes(x=1.65, y = ypos, label = percent(prop)), color = "black", size=2.8) +
  scale_fill_brewer(palette = "Set3") + 
  labs(fill = "Region", title = "Proportion of Restaurants in Toronto by Borough") +
  theme(plot.title = element_text(face = "bold"))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
library(dplyr)
library(palettetown)
library(RColorBrewer)
library(ggthemes)
library(scales)
library(broom)
library(purrr)
devtools::install_github("johannesbjork/LaCroixColoR")
library(LaCroixColoR)

@@

### Create pie chart
ggplot(dfBoroughs, aes(x="", y = prop, fill = group)) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  coord_polar("y", start = 0) +
  geom_text(aes(x=1.65, y = ypos, label = percent(prop)), color = "black", size=2.8) +
  scale_fill_manual(values=lacroix_palette("PeachPear", n = 9)) + 
  labs(fill = "Region", title = "Proportion of Restaurants in Toronto by Borough") +
  theme(plot.title = element_text(face = "bold")) +
  theme_void() +
  theme(plot.title = element_text(face = "bold"))
```
